ManuscriptFigures

### 2024-03-13 Code/Plots_Growth.Rmd
Generated .tiff

ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = MIT9313PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
